\documentclass[a4paper, 12pt]{article}

\newlength{\lineseparation}
\setlength{\lineseparation}{1cm}

\usepackage{setspace}
\usepackage{fullpage}

\begin{document}


\Large
\tt

 ok-voon ororok sprok . \\[\lineseparation]

 at-voon bichat dat .

\hrulefill

 ok-drubel ok-voon anok plok sprok . \\[\lineseparation]


 at-drubel at-voon pippat rrat dat . 

\hrulefill

 erok sprok izok hihok ghirok . \\[\lineseparation]


 totat dat arrat vat hilat . 

\hrulefill

 ok-voon anok drok brok jok . \\[\lineseparation]


 at-voon krat pippat sat lat . 

\hrulefill

 wiwok farok izok stok . \\[\lineseparation]


 totat jjat quat cat . 

\hrulefill

 lalok sprok izok jok stok . \\[\lineseparation]


 wat dat krat quat cat . 


 lalok farok ororok lalok sprok izok enemok . \\[\lineseparation]


wat jjat bichat wat dat vat eneat . 


\hrulefill

 lalok brok anok plok nok . \\[\lineseparation]


 iat lat pippat rrat nnat . 

\hrulefill

 wiwok nok izok kantok ok-yurp . \\[\lineseparation]


 totat nnat quat oloat at-yurp . 

\hrulefill

 lalok mok nok yorok ghirok clok . \\[\lineseparation]


 wat nnat gat mat bat hilat . 

\hrulefill

 lalok nok crrrok hihok yorok zanzanok . \\[\lineseparation]


 wat nnat arrat mat zanzanat . 

\hrulefill

 lalok rarok nok izok hihok mok . \\[\lineseparation]


 wat nnat forat arrat vat gat . 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{
\rm

\textbf{arrat:} hihok

\textbf{at-drubel:} ok-drubel

\textbf{at-voon:} ok-voon

\textbf{at-voon:} ok-voon

\textbf{at-yurp:} ok-yurp

\textbf{bat:} clok

\textbf{bichat:} ororok

\textbf{cat:} stok

\textbf{dat:} sprok

\textbf{eneat:} enemok

\textbf{forat:} rarok

\textbf{gat:} mok

\textbf{hilat:} ghirok

\textbf{iat:} lalok

\textbf{jjat:} farok

\textbf{krat:} jok

\textbf{lat:} drok, brok

\textbf{mat:} yorok

\textbf{nnat:} nok

\textbf{oloat:} kantok

\textbf{pippat:} anok

\textbf{quat:} izok

\textbf{rrat:} plok

\textbf{sat:} drok, brok

\textbf{totat:} erok, wiwok

\textbf{vat:} izok, lalok

\textbf{wat:} lalok

\textbf{zanzanat:} zanzanok
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Garcia and associates. \\[\lineseparation]

Garcia y asociados.

\hrulefill

Carlos Garcia has three associates. \\[\lineseparation]

Carlos Garcia tiene tres asociados.

\hrulefill

his associates are not strong. \\[\lineseparation]

sus asociados no son fuertes.

\hrulefill

Garcia has a company also. \\[\lineseparation]

Garcia tambien tiene una empresa.

\hrulefill

its clients are angry. \\[\lineseparation]

sus clientes est\'an enfadados.

\hrulefill

the associates are also angry. \\[\lineseparation]

los asociados tambien est\'an enfadados.

\newpage

the clients and the associates are enemies. \\[\lineseparation]

los clientes y los asociados son enemigos.

\hrulefill

the company has three groups. \\[\lineseparation]

la empresa tiene tres grupos.

\hrulefill

its groups are in Europe. \\[\lineseparation]

sus grupos est\'an en Europa.

\hrulefill

the modern groups sell strong pharmaceuti- cals. \\[\lineseparation]

los grupos modernos venden medicinas fuertes.

\hrulefill

the groups do not sell zanzanine. \\[\lineseparation]

los grupos no venden zanzanina.

\hrulefill

the small groups are not modern. \\[\lineseparation]

los grupos peque\~nos no son modernos.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\rm

iat lat pippat eneat hilat oloat ay-yurp .

\textbf{la empresa tiene enemigos fuertes en Europa .}

lalok brok anok ghirok enemok kantok ok-yurp .

\textbf{the company has strong enemies in Europe .}

\hrulefill

totat nnat forat arrat mat bat .

\textbf{sus grupos peque\~nos no venden medicinas .}

wiwok rarok nok crrrok hihok yorok clok .

\textbf{its small groups do not sell phramaceuticals.}

\hrulefill

wat dat quat cat uskrat at-drubbel .

\textbf{los asociados est\'an enfadados con Carlos .}

lalok sprok izok stok ? ok-drubbel .

\textbf{the associates are angry ? Carlos .}

\end{document}
